Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-18 concurrency/CONCUR 2023/paper.tex
modified specs

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			 \forall \  \texttt{t}. \left\langle
			\begin{array}{c}
				\nodeboxrep \texttt{(pn->n)}  \ \ast \ \texttt{R(pn->n)} \ \big| \ \treerep\ \texttt{t}
			\end{array}
			\right\rangle
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\langle \exists \  \texttt{res} \ \texttt{n'}.
			\begin{array}{c}
				\ \texttt{(res} \leftrightarrow (\texttt{pn->n'->t} = \texttt{NULL))}  \ \ast \ \nodeboxrep \texttt{(pn->n')} \\  
				\ast \ \texttt{R(pn->n')} \ast \ \texttt{(k} \in \texttt{range(n'))}
			\end{array}
			\ \Bigg| \ \treerep\ \texttt{t}
			\right\rangle
		}
	\end{mathpar}
	\caption{Specification of \texttt{traverse} for the lock-coupling template}
	\label{fig:traverse_lock}
\end{figure}
%\than{Actually, $\nodeboxrep \texttt{(pn->n)}$ and $\texttt{data\_at  n pn} \ast \texttt{my\_half g\_root} (-\inf, +\inf)$ is equivalent to $\texttt{tree\_rep}$. But now we can ignore the information of $\texttt{my\_half}$.  }

@@

The atomic specification for \texttt{insert} method is
\begin{mathpar}
	{\color{blue}\langle \texttt{m}.\ \nodeboxrep\ \texttt{p} \ |\ \treerep\ \texttt{m}\rangle } \ \ \texttt{insert(p, k, v)}\ 
	{\color{blue}\langle \nodeboxrep\ \texttt{p}\ |\ \treerep\ (\texttt{m[k} \mapsto \texttt{v])}\rangle }
\end{mathpar}

@@

\begin{figure}
	\centering
\begin{mathpar}
	% spec of inRange
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n} \ \ast \texttt{n->t} \ \ast \ \texttt{n->min} \ \ast \ \texttt{n->max}
		\end{array}
		\right\}
	}
	\\ 
	\texttt{inRange(pn, k)} 
	\\
	{\color{blue}
		\left\{\exists \  \texttt{res.}
		\begin{array}{c}
			 \ \texttt{pn->n} \ \ast \ \texttt{n->t} \ \ast \ \texttt{n->min} \ \ast \ \texttt{n->max}\  \ast \\ 
			\ \texttt{(if res then } \texttt{(min < x} \land \texttt{x < max)} \land \texttt{(x} \leq \texttt{min} \lor \texttt{x} \geq \texttt{max))}
		\end{array}
		\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{inRange} for the give-up template}
\label{fig:inRange_giveup}
\end{figure}

\begin{figure}
	\centering
	\begin{mathpar}
	%spec of insertOp
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n} \ \ast \texttt{n->t} \  \ast \texttt{n->min} \ \ast \texttt{n->max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
	\left\{\exists \ \texttt{t' l r lk1 lk2}. 
	\begin{array}{l}
		\ \texttt{pn->n} \ \ast \ \texttt{n->t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \ \ast \ \\
		\ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, x))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (x, max))}
	\end{array}
	\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{insertOp} for the give-up template}
\label{fig:insertOp_giveup}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			 \forall \  \texttt{m}. \left\langle
				\nodeboxrep \texttt{(pn->n)}  \ \ast \ \texttt{R(pn->n)} \ \big| \ \treerep\ \texttt{m} \
			\right\rangle
		}
		\\ 
		\texttt{insertOp(pn, k, v)} 
		\\
		{\color{blue}
			\left\langle \exists \  \texttt{res} \ \texttt{n'}.
			\begin{array}{c}
				\ \texttt{(res} \leftrightarrow (\texttt{pn->n'->t} = \texttt{NULL))}  \ \ast \ \nodeboxrep \texttt{(pn->n')} \\  
				\ast \ \texttt{R(pn->n')} \ast \ \texttt{(k} \in \texttt{range(n'))}
			\end{array}
			\ \Bigg| \ \treerep\ \texttt{m} \
			\right\rangle
		}
	\end{mathpar}
	\caption{Specification of \texttt{traverse} for the lock-coupling template}
	\label{fig:traverse_lock}
\end{figure}
%\than{Actually, $\nodeboxrep \texttt{(pn->n)}$ and $\texttt{data\_at  n pn} \ast \texttt{my\_half g\_root} (-\inf, +\inf)$ is equivalent to $\texttt{tree\_rep}$. But now we can ignore the information of $\texttt{my\_half}$.  }

@@

The atomic specification for \texttt{insert} method is
\begin{mathpar}
	{\color{blue}
		\texttt{m.}\left\langle 
		\nodeboxrep\ \texttt{p} \ \big | \ \treerep\ \texttt{m}
		\right\rangle
	}
	\ \texttt{insert(p, k, v)}\ 
	{\color{blue}
		\left\langle 
		\nodeboxrep\ \texttt{p} \ \big | \ \treerep\ (\texttt{m[k} \mapsto \texttt{v])}
		\right\rangle
	}
\end{mathpar}

@@

\begin{figure}
	\centering
\begin{mathpar}
	% spec of inRange
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n} \ \ast \texttt{n->t} \ \ast \ \texttt{n->min} \ \ast \ \texttt{n->max}
		\end{array}
		\right\}
	}
	\\ 
	\texttt{inRange(pn, k)} 
	\\
	{\color{blue}
		\left\{\exists \  \texttt{res.}
		\begin{array}{c}
			 \ \texttt{pn->n} \ \ast \ \texttt{n->t} \ \ast \ \texttt{n->min} \ \ast \ \texttt{n->max}\  \\ 
			 \ \ast  \ \texttt{(if res then } \texttt{(min < x} \land \texttt{x < max)} \land \texttt{(x} \leq \texttt{min} \lor \texttt{x} \geq \texttt{max))}
		\end{array}
		\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{inRange} for the give-up template}
\label{fig:inRange_giveup}
\end{figure}

\begin{figure}
	\centering
	\begin{mathpar}
	%spec of insertOp
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn->n} \ \ast \texttt{n->t} \  \ast \texttt{n->min} \ \ast \texttt{n->max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
	\left\{\exists \ \texttt{t' l r lk1 lk2}. 
	\begin{array}{c}
		\ \texttt{pn->n} \ \ast \ \texttt{n->t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
		\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, x))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (x, max))}
	\end{array}
	\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{insertOp} for the give-up template}
\label{fig:insertOp_giveup}
\end{figure}
